Cover letter for the original IJRR submission

### 2017-12-12 review_tro_2/reviewer_response.tex

\quot {... and to refer
to the underlying method used by the Blender tool.}

\as{TODO}

\section{Answers to Reviewer 1}
%~ \ndone reecriture p3 + enlever main video

\quot{First of all, I would like to thank the authors for the significant
improvements to the paper. The contributions are much clearer, the
algorithms are better described, and I believe that my initial concerns
about the paper have been addressed. In particular, I would like to
thank the authors for the detailed inline responses.}

\as{We in turn thank the reviewer, who significantly helped us improving the paper with his comments.}

\leavevmode \\
\quot {It looks like that sentence was not actually removed from the
paper (referring to the sentence ``optimization-based approaches
only converge locally'')
}

\as{Indeed, the sentence was somehow not removed from our latest version. We apologize for that, and guarantee that this time it was indeed removed!}

\leavevmode \\
\quot {
The dual reformulation of the LP in (11) in Sect. VI is fine, but is
a perfectly standard procedure (that, in fact, many LP solvers will
perform internally automatically). It would be sufficient to mention
that the dual problem is solved without giving its full formulation.
Whether the authors include the formulation is up to them.}

@@

\as{Thanks for the comment. Indeed, using the dual formulation is quite common for LP solvers. However, after computing the dual in our case, it turns out that some of the constraints can be solved trivially, which allows to reduce the dimensionality of the problem, resulting in (11). We experimentally verified that this form is faster to solve with respect to the one from equation (10). For this reason, we believe that equation (11) is worth mentioning, and prefer to leave it, since it was given as an option by the reviewer. Finally, we removed the reference to the Slater's conditions since we agree with the reviewer that the procedure is standard.}

\leavevmode \\
\section{Answers to Reviewer 2}
\quot{All the issues I raised in the first review have been addressed in
the revised version. I'm satisfied with most of the answers and the
changes made to the paper. In particular the novelty of the paper with
respect to the conference works is clarified. I appreciate also the new
structure of the manuscript that integrates material previously
relegated to the Appendices into the main body. Now, this work seems to
be self contained enough for a journal. }
\as{Thanks for the comment. We agree with the reviewer that the paper is better this way.}

\leavevmode \\
\quot{
1. I understand the point of view of the authors who focus on
multi-contact planning and would like to refer only briefly to previous
work in motion planning for multi-legged, statically-stable robots. In
principle that is OK, but I suggest to extend the paragraph added at
the end of Section I.A by few sentences that clarify what are the
advantages of your motion planning system with respect to these older
approaches. You are focusing on humanoids, for which these gains are
pretty obvious, but what about multi-legged robots? As an inspiration I
recommend this youtube video showing a simulated hexapod that does
something similar to your HyQ simulated example
\url{https://www.youtube.com/watch?v=Xio1TbjAK80}}

\as{TODO}
\leavevmode \\

\quot{
While the answer about the environment model is satisfying, I think
that you should no only refer to the FCL library in a footnote, but to
cite the paper that explains how it works:
http://ieeexplore.ieee.org/document/6225337/?reload=true
}
\as{Thanks for the suggestion. The citation has indeed been included, as reference TODO}
\leavevmode \\

### 2017-12-12 body/contact.tex
reviewer 2 comment 2 fcl

We define $C_{Contact}^{\epsilon} \supset C_{Contact}$ as the set of configurations such that the minimum 3D distance 
between an effector and an obstacle is less than $\epsilon \in \mathbb{R}$.
We then apply the following steps:
\begin{enumerate}
\item Generate off-line $N$ valid sample limb configurations $\mathbf{q}^k_i,  0 \leq i < N$ (We choose $N=10^4$);
\item Using the end-effector positions $\mathbf{p}(\mathbf{q}^k_i)$ as indices, store each sample in an octree data structure;
\item At runtime, when contact creation is required, intersect the octree and the environment\footnote{this operation is achieved natively by the fcl library https://flexible-collision-library.github.io/} to retrieve the list of samples $S \subset C_{Contact}^{\epsilon}$ close to contact (Figure~\ref{fig:contact_gen} (b) and (c));
\item Use a user-defined heuristic $h$ to sort $S$;
\item If $S$ is empty, stop (failure). Else select the first configuration of $S$. Project it onto contact using inverse kinematics. (Figure~\ref{fig:contact_gen} (d) and (e));
\item If Eq.~\ref{eq:contact_gen} is verified, stop (success). Otherwise remove the element from $S$ and go to step 5.
\end{enumerate}

>>>>

We define $C_{Contact}^{\epsilon} \supset C_{Contact}$ as the set of configurations such that the minimum 3D distance 
between an effector and an obstacle is less than $\epsilon \in \mathbb{R}$.
We then apply the following steps:
\begin{enumerate}
\item Generate off-line $N$ valid sample limb configurations $\mathbf{q}^k_i,  0 \leq i < N$ (We choose $N=10^4$);
\item Using the end-effector positions $\mathbf{p}(\mathbf{q}^k_i)$ as indices, store each sample in an octree data structure;
\item At runtime, when contact creation is required, intersect the octree and the environment to retrieve the list of samples $S \subset C_{Contact}^{\epsilon}$ close to contact (Figure~\ref{fig:contact_gen} (b) and (c)). This operation is achieved natively by the fcl library \cite{6225337};
\item Use a user-defined heuristic $h$ to sort $S$;
\item If $S$ is empty, stop (failure). Else select the first configuration of $S$. Project it onto contact using inverse kinematics. (Figure~\ref{fig:contact_gen} (d) and (e));
\item If Eq.~\ref{eq:contact_gen} is verified, stop (success). Otherwise remove the element from $S$ and go to step 5.
\end{enumerate}
